Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-25 paper/paper.Rmd
added conceptual paragraph on spatial CV types

- add a paragraph with more information on spCV using spatial partitionings

>>>>

Approaches based on spatial blocking or grouping require either the construction of spatial zones, or the use of pre-existing spatial structures in the data. Let's refer to these spatial units or zones as $\mathcal{Z_i}$, $1\le i\le n_z$. 
These zones are often constructed to serve as the $k=n_z$ spatial partitions, for example by performing $k$-means clustering of the sample coordinates (ref??) or generating the desired number of rectangular blocks. 
However, when $n_z$ is much larger than the desired number of folds, $k$, then a partitioning can be applied to the zones, i.e. the indices $1, \ldots, n_z$ are grouped into $k$ equally sized subsets $\mathcal{I}_1, \ldots, \mathcal{I}_k$.
This approach has been applied, for example, in spatial CV at the agricultural field level (Pena??) or at the transect level (Kasurak??).
In the following we will conceptually distinguish between CV *at the group (or block) level*, referring to the latter scenario, from spatial *block (or group)* CV, where the blocks or groups themselves define the CV partitions.
